Comparison with Christensen paper

### 2018-12-20 paper-comparison/compare-christensen.Rmd
knit through ldats on ldats

```{r rodent data comparison}

@@

```{r data adjustment cleanup, include = FALSE}
rm(list = c('diagnose_dat', 'nplots', 'compare', 'compare_raw', 'adjusted_table', 'i', 'compare_rows', 'raw_table', 'create_rodent_table'))
```

@@

ldats_dat <- as.matrix(ch_dat)
ldats_dat <- apply(ldats_dat, c(1,2), FUN = as.integer)
rodents$document_term_table <- ldats_dat
rm(ldats_dat)
rm(ldats_dates)

@@

```{r LDATS LDAs}

@@

```{r paper LDAs}
source('christensen-ecology-files/AIC_model_selection.R')
source('christensen-ecology-files/LDA-distance.R')

@@

```{r plot LDAs}
# Paper
LDA_plot_top_panel(ldamodel, cols = NULL, option = "D")

# LDATS
LDA_plot_top_panel(ldats_lda_selected[[1]], cols = NULL, option = "D")
```

## Changepoint

>>>>

```{r rodent data comparison, eval = F}

@@

```{r data adjustment cleanup, eval = F, include = FALSE}
rm(list = c('diagnose_dat', 'nplots', 'compare', 'compare_raw', 'adjusted_table', 'i', 'compare_rows', 'raw_table', 'create_rodent_table'))
```

@@

ldats_dat <- as.matrix(ch_dat)
ldats_dat <- apply(ldats_dat, c(1,2), FUN = as.integer)
rodents$document_term_table <- ldats_dat
rm(ldats_dat)
rm(ldats_dates)
rm(ch_dates)
rm(ch_dat)
```

@@

```{r LDATS LDAs, eval = F}

@@

```{r paper LDAs, eval = F}
source('christensen-ecology-files/AIC_model_selection.R')
source('christensen-ecology-files/LDA-distance.R')

@@

```{r save LDAs, eval = F, include = F}
save(ldamodel, file = 'model-stash/paper_lda.Rds')
save(ldats_lda_selected, file = 'model-stash/ldats_lda.Rds')
```

```{r reload LDAS, include = FALSE}

load('model-stash/ldats_lda.Rds')
load('model-stash/paper_lda.Rds')

### Plot LDAS

```{r plot LDAs}
# Paper
plot(ldamodel, cols = NULL, option = "D")

# LDATS
plot(ldats_lda_selected[[1]], cols = NULL, option = "D")
```

## Changepoint models

I am going to compare four combinations of LDA + changepoint models:

* LDATS LDA + LDATS changepoint
* LDATS LDA + paper changepoint
* Paper LDA + LDATS changepoint
* Paper LDA + paper changepoint

There is the additional wrinkle of `document_term_weights`. The paper weighted all sample periods equally, wheras LDATS can weight sample periods according to how many individuals were captured. We now believe it is more appropriate to weight periods proportional to captures. However, for the purposes of comparison, I will continue to set all weights = 1 for both changepoint models. For an example of LDATS run with proportional weights, see the rodents vignette. [?]

### LDATS LDA with LDATS changepoint
```{r, include = F}
# remove paper LDA (for memory)
rm(ldamodel)
```

```{r LDATS LDA + LDATS cpt}
# Run changepoint

ldats_ldats <- LDATS::TS_on_LDA(LDA_models = ldats_lda_selected,
                                document_covariate_table = rodents[[2]],
                                formulas =c(~ sin_year + cos_year),
                                nchangepoints = c(2, 3),
                                weights = NULL)

save(ldats_ldats, file = 'model-stash/ldats_ldats.Rds')

# Select best changepoint

ldats_ldats_selected <- LDATS::select_TS(TS_models = ldats_ldats)

save(ldats_ldats_selected, file = 'model-stash/ldats_ldats_selected.Rds')
